### 2009-01-08 pkg/docs/SpatialFun/code.Rnw
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@19 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

library(glmmBUGS)
data(popDataAdjMat)

@@

ontario = mergeBugsData(ontario, ontarioSummary)
head(ontario@data)
spplot(ontario, "RCSDUIDSpatial.mean")

>>>>

library(glmmBUGS)
data(popDataAdjMat)
library(spdep)
popDataAdjMat = poly2nb(ontario, row.names=as.character(ontario$CSDUID))

@@

ontario = mergeBugsData(ontario, ontarioSummary)
head(ontario@data)
spplot(ontario, "RCSDUIDSpatial")
